---
title: "NetworkConstruction"
author: "Mehdi Merbah"
date: "4/8/2021"
output: html_document
---

```{r setup, results='hide'}
#knitr::opts_chunk$set(echo = TRUE)
library(GENIE3)
library(WGCNA)
library(igraph)
library(print)
#library(Rgraphviz)
```



## GENIE3

### Extracting Regulatory Realtionships
```{r eval=FALSE, include=FALSE}
network_matrix <- rounded[common_genes,]
weight_matrix <- GENIE3(as.matrix(network_matrix))
weight_matrix[1:5,1:5]
gene_link_list <- getLinkList(weight_matrix, threshold = 0.05)
gene_link_list
reg_genes <- gene_link_list$regulatoryGene
```

```{r}
stand_alone_DE <- subset(expRes_4v2, padj<0.05 & abs(log2FoldChange)>2.5)
stand_alone_gene_list <- rownames(stand_alone_DE)
length(stand_alone_gene_list)
test_network_matrix <- rounded[stand_alone_gene_list,]
test_weight_matrix <- GENIE3(as.matrix(test_network_matrix))
test_weight_matrix[20:25,21:25]
test_gene_link_list <- getLinkList(test_weight_matrix, threshold = 0.05)
test_gene_link_list

```
```{r}
test_weight_matrix[20:25,21:25]
print(xtable(test_weight_matrix, type = "latex"), file = "weights.tex")
```


### Network Visualization
```{r echo=TRUE}
graph_data <- graph.data.frame(test_gene_link_list, directed = F)
adj_list <- get.adjacency(graph_data, sparse = T, attr = "weight", type = "both")

adj_graph <- graph.adjacency(adj_list, mode = "undirected", weighted = T)

#graph.isomorphic(g, g_arasi)
png("network.png", units="in", width=5, height=5, res=300)

plot(adj_graph, vertex.color="grey", vertex.size=12, vertex.frame.color="grey", vertex.label.family="Arial", vertex.label.color="black", vertex.label.cex=0.2, vertex.label.dist=0, vertex.label.font=1.5, edge.curved=0.2, edge.color="red")
#dev.off()
```




## WGCNA

Loading the modules and setting up the environement  
```{r}
library(WGCNA)
options(stringsAsFactors =  FALSE)
enableWGCNAThreads()
```

Constructing a weighted gene network necessitates the choice of a thresholding power \beta that we raise the co-expression similarity to infer the adjacency. The authors of the original WGCGNA paper suggested to use this power based on the criterion of (approximate scale-free topology ?)  

```{r}
# First we pick soft thresholding powers
powers <- c(seq(1,10,by=1), seq(12,20, by=2))
# Network topology analysis function
sft <- pickSoftThreshold(network_matrix, powerVector= powers, verbose = 5)
sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.90,col="red")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")

```

```{r}
softPower = 6
adjacency_mat <- adjacency(t(network_matrix), power = softPower)
TOM = TOMsimilarity(adjacency_mat);
dissTOM = 1 - TOM

# Call the hierarchical clustering function
geneTree = hclust(as.dist(dissTOM), method = "average");
# Plot the resulting clustering tree (dendrogram)
sizeGrWindow(12,9)
plot(geneTree, xlab="", sub="", main = "Gene clustering on TOM-based dissimilarity",labels = FALSE, hang = 0.04)
```


```{r}
minModuleSize = 20;
# Module identification using dynamic tree cut:
dynamicMods = cutreeDynamic(dendro = geneTree, distM = dissTOM, deepSplit = 2, pamRespectsDendro = FALSE, minClusterSize = minModuleSize);
table(dynamicMods) 

```

```{r}
dynamicColors = labels2colors(dynamicMods)
table(dynamicColors)
# Plot the dendrogram and colors underneath
sizeGrWindow(8,6)
plotDendroAndColors(geneTree, dynamicColors, "Dynamic Tree Cut",
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05,
main = "Gene dendrogram and module colors")

# Calculate eigengenes
MEList = moduleEigengenes(t(network_matrix), colors = dynamicColors)
MEs = MEList$eigengenes
# Calculate dissimilarity of module eigengenes
MEDiss = 1-cor(MEs);
# Cluster module eigengenes
METree = hclust(as.dist(MEDiss), method = "average");
# Plot the result
sizeGrWindow(7, 6)
plot(METree, main = "Clustering of module eigengenes",
xlab = "", sub = "")
MEDissThres = 0.25
# Plot the cut line into the dendrogram
abline(h=MEDissThres, col = "red")
# Call an automatic merging function
merge = mergeCloseModules(t(network_matrix), dynamicColors, cutHeight = MEDissThres, verbose = 3)
# The merged module colors
mergedColors = merge$colors;
# Eigengenes of the new merged modules:
mergedMEs = merge$newMEs;
```

```{r}
sizeGrWindow(12, 9)
#pdf(file = "Plots/geneDendro-3.pdf", wi = 9, he = 6)
plotDendroAndColors(geneTree, cbind(dynamicColors, mergedColors),
c("Dynamic Tree Cut", "Merged dynamic"),
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05)
```



## Mutual Information







