---
title: "PathwayAnalysis"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Loading Packages
```{r}
library(pathview)
library(gage)
#library(gageData)
suppressWarnings(library(enrichR))
suppressWarnings(library(ggplot2))
```


## Gene Set Enrichment Analysis

        The following is GSEA performed using the enrichR package focused on 6 databases:GO Bio. Processes/Molecular Functions, KEGG, Reactome, Wiki Pathways and Elsevier Pathways. The goal is to see if there are any common pathways or biological functions/processes between the differentially expressed genes from the DEA of different grade contrasts. 

        We first construct the enrichment sets with enrichR and plot them for every grade comparison.
```{r}
# Geneset enrichment with enrichR
dbs <- c("Reactome_2016", "KEGG_2021_Human", "WikiPathway_2021_Human", "Elsevier_Pathway_Collection")
enriched_4v2 <- enrichr(gene_list_4v2, dbs)
enriched_4v3 <- enrichr(gene_list_4v3, dbs)
enriched_3v2 <- enrichr(gene_list_3v2, dbs)
enriched_common <- enrichr(common_genes, dbs)

```
### Common Genes GSEA
```{r}
plotEnrich(enriched_common[[4]], title= "Enrichment Common Genes")
head(enriched_common[[4]][c("Term","P.value","Genes")], 10)
```

### Grades 2v3

```{r}
plotEnrich(enriched_3v2[[1]], title= "Enrichment 3 vs 2")
```


### Grades 4v2
```{r}
plotEnrich(enriched_4v2[[4]], title= "Enrichment 4 vs 2")
head(enriched_4v2[[4]][c("Term","P.value","Genes")], 10)
```


### Grades 4v3

```{r}
plotEnrich(enriched_4v3[[1]], title= "Enrichment 4 vs 3")
```



### Unique Genes in Grades intersects
#### 4V2
```{r}
enriched_4v2_exclusive <- enrichr(genes_4v2_excluding_intersect, dbs)
plotEnrich(enriched_4v2_exclusive[[4]], title= "Enrichment 4 vs 2 Exclusive")
```


#### 3v2 and 4v2 excluding common to all

```{r}
enriched_4v2_exclusive <- enrichr(genes_3v2and4v2_excluding_intersection, dbs)
plotEnrich(enriched_4v2_exclusive[[4]], title= "Enrichment 4v2 and 3v2 Exclusive")
```


##ID MAPPING
```{r}
library(org.Hs.eg.db)
hommo_sapiens <- org.Hs.eg.db
common_genes_entrezIDs <- select(hs, 
       keys = common_genes,
       columns = c("ENTREZID", "SYMBOL"),
       keytype = "SYMBOL")

common_genes_entrezIDs

grade4v2_entrezIDs <- select(hs, 
       keys = gene_list_4v2,
       columns = c("ENTREZID", "SYMBOL"),
       keytype = "SYMBOL")
grade4v2_entrezIDs <- na.omit(grade4v2_entrezIDs)
grade4v2_entrezIDs
```


##KEGG

```{r}
kegg_enriched <- enriched_common[3]
KEGG_IDs <- mget(as.character(common_genes_entrezIDs$ENTREZID), org.Hs.egPATH, ifnotfound = NA)
kegg_IDs_4v2 <- mget(as.character(grade4v2_entrezIDs$ENTREZID), org.Hs.egPATH, ifnotfound = NA)
```

## Reactome
```{r}
reactomeEnriched_4v2 <- ReactomePA::enrichPathway(grade4v2_entrezIDs$ENTREZID,  readable = TRUE)
reactomeEnriched_common <- ReactomePA::enrichPathway(common_genes_entrezIDs$ENTREZID, readable = TRUE)
head(reactomeEnriched_4v2[,c("Description","geneID")], 40)
head(reactomeEnriched_common[,c("Description","geneID")])
#ReactomePA::viewPathway("Signaling by Interleukins", readable = TRUE)
```

